FEM Model Analysis

### 2021-09-10 FEM_R/model_analysis_core.Rmd
Moved AgeUK validation data into the E_FEM filesystem (previously sat 1 level up). Changed paths in model_analysis_core.Rmd to point to new directory

```{r echo = FALSE}
#AgeUK
male_au <- read.csv('../Validation/AgeUK-chronDisease-MALE_CI.csv')
female_au <- read.csv('../Validation/AgeUK-chronDisease-FEMALE_CI.csv')

# FEM 2014 summary
FEM <- read_dta('output/COMPLETE/ELSA_AgeUK_core_valid/ELSA_AgeUK_core_valid_summary.dta')

@@

```{r echo=False}
FEM_base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')

@@

ggsave(filename = 'smoking_prev_2018.png',
       plot = smok.plot,
       path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/validation/',
       width = 7,
       height = 5)

>>>>

```{r echo = FALSE}
#AgeUK
male_au <- read.csv('../../FEM_R/AgeUK_Validation/AgeUK-chronDisease-MALE_CI.csv')
female_au <- read.csv('../../FEM_R/AgeUK_Validation/AgeUK-chronDisease-FEMALE_CI.csv')

# FEM 2014 summary
FEM <- read_dta('ELSA_AgeUK_core_valid/ELSA_AgeUK_core_valid_summary.dta')

@@

```{r echo=FALSE}
FEM_base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')

@@

#ggsave(filename = 'smoking_prev_2018.png',
#       plot = smok.plot,
#       path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/validation/',
#       width = 7,
#       height = 5)
